\item Schmidt - \lokiquote{fdtc-2008-schmidt}

\textbf{Paper's sum-up:}\\
Present a FI attack breaking straightforward RSA skipping squarrings.
Applicable to most the exponentiation algorithm. 


\textbf{Summing up \textit{Attack}} LtoR S\&M

\underline{Fault model:}
be able to skipp a determined squaring.

\underline{Targetted:}
RtoL \& LtoR: S\&M, S\&MA, $2^k$-arry method, sliding window.

\underline{Type of attack:}
random known plaintext attack $\&$ reproducible input attack, 
correct signature mandatory. 

\underline{Counter measures}
Ineffective: Square \& Multiply always.
Effective: the authors are claiming that they can overcome 
'most of SPA countermeasure' by skipping the phase where this counter
measure is applied. With their super fault model this trivial:
-'each time that I want to skipp an operation it works'-. 
Practically, 'most of SPA countermeasure' defeats this attack.

Initialization:\\
get $Sig_0$ -skip the last squaring- and the correspondent non faulted signature.\\
Then, if the last square has been genuinely skipped, we shall have:
\begin{center}
$
Sig = \left\{
    \begin{array}{ll}
        {Sig_0}^2 \mod n & \textsf{ for } e_0=0 \\
        {Sig_0}^2 \times m^{-1}  \mod n & \textsf{ for } e_0=1 \\
    \end{array}
\right.
$
\end{center}
Do this operation till the previous equation has been verified and then $e_0$ deduced.

Induction:\\
Then when all the first $k-1$ bit of the exponent has been obtained, 
if the right square has been genuinely skipped, we shall have:
\begin{center}
$
Sig_k = \left\{
    \begin{array}{ll}
        {Sig_{k-1}} \mod n & \textsf{ for } e_{k-1}=0 \\
        {Sig_{k-1}} \times m^{2^{k-1}}  \mod n & \textsf{ for } e_{k-1}=1 \\
    \end{array}
\right.
$
\end{center}

